### 2018-10-08 doc/results.tex

% effects, time series
\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio=true]{figure/effect_time_group}
  \caption{Effects of the four covariates as estimated for all time intervals and for each phyla. For each time series, the red line corresponds to the median estimate for each interval, while the envelopes represent various credible intervals as labeled.}
  \label{fig:effect_time_group}
\end{figure}

@@

Figure \ref{fig:hazard_baselin} is a graph of the average hazard associated with age of observation. This graph illustrates how average extinction risk increases with age for the first few million years before leveling off. A species reaches highest age-related probability of extinction at 10 million years, after which the median becomes volatile until a duration over 30 million years. The flat-ness of the median estimate and the homogeneity of variance durations between approximately 30 million years to under 60 million years is due to the lack of species having survived over 30 million years, which inherently means that these estimates are based on less information and are shrunk towards the overall average while reflecting more and more of our prior uncertainty over time.

@@

Optimal cutpoint between 0.1 and 0.11 percent. We estimate that the effect of age of observation on extinction can reach this threshold after XX My at ##\% posterior probability.

@@

This result means that, given this model, the greatest contributor to changes in extinction risk over time is when a species is present. In comparison, the covariates we studied individually contribute only a limited amount to the variation in extinction. Similarly, while age at observation does contribute to some differences in extinction risk (Fig XXX age effect), this effect is most likely overwhelmed by the importance of when that observation takes place.

@@

>>>>

% effects, time series
\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio=true]{figure/eff_time_group}
  \caption{Effects of the four covariates as estimated for all time intervals and for each phyla. For each time series, the red line corresponds to the median estimate for each interval, while the envelopes represent various credible intervals as labeled.}
  \label{fig:effect_time_group}
\end{figure}

@@

Figure \ref{fig:hazard_baseline} is a graph of the average hazard associated with age of observation. This graph illustrates how average extinction risk increases with age for the first few million years before leveling off. A species reaches highest age-related probability of extinction at 10 million years, after which the median becomes volatile until a duration over 30 million years. The flat-ness of the median estimate and the homogeneity of variance durations between approximately 30 million years to under 60 million years is due to the lack of species having survived over 30 million years, which inherently means that these estimates are based on less information and are shrunk towards the overall average while reflecting more and more of our prior uncertainty over time.

@@

Optimal cutpoint between 0.1 and 0.11 percent. We estimate that the effect of age of observation on extinction can reach this threshold after XX My at YY\% posterior probability.

@@

This result means that, given this model, the greatest contributor to differences in extinction risk over time is when a species is present. In comparison, the covariates we studied individually contribute only a limited amount to the variation in extinction. Similarly, while age at observation does contribute to some differences in extinction risk (Fig XXX age effect), this effect is most likely overwhelmed by the importance of when that observation takes place.

The variance in effects contributed by the phyla is approximately equal to the variance in those effects due to differences over time.

@@

Looking at four randomly sampled species, we evaluated their probability of extinction at all times that species was observed. We then compared these estimates to the geographic range trajectory of
